---
title: "p8105_hw1_lz2951"
author: "lz2951"
output: github_document
date: "2023-09-22"
---

# Problem 1

## Load package and data

```{r}
library(moderndive)
library(tidyverse)
data("early_january_weather")
```

## Short description of dataset

According to the dataset help file, we could know that this dataset is hourly meterological data for LGA, JFK and EWR for the month of January 2013. Following is some key information about this dataset:

1. The variables in the dataset are `r names(early_january_weather)`. The values of a important variable 'temp' are `r early_january_weather$temp`.
2. The dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.
3. The mean of variable 'temp' is `r mean(early_january_weather$temp)`.

## Make a scatterplot and describe it

Make a scatterplot using time_hour as x and temp as y; color points using humid. 

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
```

Accordig top the scatterplot, from 2013-01-01 to 2013-01-15:
1. The temperature went up and down within a single day because of sunrise and sunset.
2. The temperature increased because of seasonal change.
3. The air became dryer as temperature increased within a day.

## Export scatterplot

```{r}
ggsave("scatter_plot.pdf")
```

